%-----------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------------------
\documentclass[12pt,letterpaper,roman]{moderncv} % Font sizes: 10, 11, or 12;
%paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or
%landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default),
%'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange',
%'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the
%template
\usepackage{verbatim}
\usepackage[scale=0.8]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the
%dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment
%to adjust the width of the space allocated to your name
%------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%------------------------------------------------------------------------------

\firstname{Shuai} % Your first name
\familyname{Wang} % Your last name

\title{Curriculum Vitae}
\address{1319 Main St}{Cincinnati, Ohio 45202}
\mobile{(937) 654 0806}
% \email{wang.172@wright.edu}
\email{vanstark88@gmail.com}
\homepage{shuaiwang88.github.io}

%------------------------------------------------------------------------------

\begin{document}
%\setlength{\parskip}{2em}
\makecvtitle % Print the CV title

%------------------------------------------------------------------------------
%	EDUCATION SECTION
%------------------------------------------------------------------------------

\section{Education}
\cventry{2011--2017}{Ph.D. in Engineering Program, Industrial and Human
System}
{Wright State University}{Dayton, Ohio}{}{}  
% Arguments not required can be left empty
%\cventry{2011--2012}{Master in Engineering and Entrepreneurship
%Program}{Wright State University}{Dayton, Ohio}{UNFINISHED}{}
\cventry{2007--2011}{Bachelor of Management, Logistics Management}{Dalian
Jiaotong University}{Dalian, China}{}{}
%\vspace*{3mm} %this will fix vertical spacing for \moderncvstyle{classic}, but
%create vertical spacing issues for other \moderncvstyle{xyz}.

%-----------

%------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%------------------------------------------------------------------------------
%\section{}
\section{Computer skills} 
\cvitem{Language}{\textsc{R}, \textsc{Python}, \textsc{Julia}, \textsc{SQL}}
\cvitem{Optimization}{\textsc{AIMMS},  \textsc{Pyomo}, \textsc{Pulp},  \testsc{Minizinc}, \textsc{JuMP}, \textsc{CPLEX}, \textsc{GUROBI}, \textsc{CBC}}
\cvitem{Machine Learning}{\textsc{Datarobot}, \textsc{H2O}, \textsc{sklearn}} 
%\cvitem{Database}{\textsc{Mysql}, \textsc{MS SQL Server}}
\cvitem{Visualization}{\textsc{Shiny},\textsc{Tableau}}
%\cvitem{Simulation}{\textsc{Arena}, \textsc{Sigma}}
%\cvitem{OS}{\textsc{Mac OS}, \textsc{Linux}, \textsc{Windows}}
%\cvitem{Big Data}{\textsc{AWS}, \textsc{Apache Spark},
%		\textsc{H2O}}


\section{Experience}
\cventry{2011--2017} {Graduate Research and Teaching
Assistant}{\textsc{Wright State University}}{Dayton, OH}{}{
\begin{itemize}
\item \textbf{PhD Dissertation: Data mining techniques and mathematical models for the optimal scholarship allocation problem for a state university}
\newline 
Main Advisors: Xinhui Zhang (Senior Director of supply chain at Alibaba), Pratik Parikh (Chair of Dept of Industrial Engineering, University of Louisville).
%\newline
\item \textbf{Teaching Assistant:}
1. Intro of Machine Learning Models. 
2. Intro of Deterministic Operations Research Models.
\end{itemize} }

%\newline
\bigskip
%\bigskip

\cventry{2017.9--Present}{Lead Data Science Consultant at Kroger and 84.51}
{\textsc{Global Associates} }{Cincinnati,OH}{}{}{
\begin{itemize}
\item \textbf{Order-picking Staff Daily Scheduling System Optimization}: 
The staff scheduling system is built to optimize the number of staff required to picking 
orders at each hour. Time-series based forecasting model was used to predict the orders. 
The project saves about  20 to 30 \% labor cost than the previous implementation. 
This is escalated as one of top priority project responding to COVID19 at Kroger.

\item \textbf{Inventory Control}:
1. I build the inventory replenishment routing model based on traveling salesman problem. 
%A novel distance metric was proposed to match the store layout. 
2. A comprehensive staff activity graph was created to track the activity, idle time. 
3. Heuristic-based restock strategy was created to alert the restock point based on BOH.


\end{itemize}
}

\bigskip

\cventry{2012--2017}{Senior Operations Research Consultant at 
Kroger}{\textsc{Kroger, partner with Wright State University }}{Cincinnati,OH}{}
{} %
{
%Role: make mathematical model, implement 
%core algorithm
% \newline{}
% \textbf{Key modeler for selected projects}:

\begin{itemize}


\item \textbf{Simulation and Optimization Improves Pharmacy Inventory Management at the Kroger Co.} From media, "The Kroger Co. aspired to improve the inventory at the company's more than 1,950 pharmacy locations. A transparent simulation and optimization model is designed for pharmacy inventory management. The system enabled the company to reduce out-of-stocks by 1.5 million prescriptions, lowered inventory by more than \$100million, and yielded additional revenue of more than \$70 million since Oct 2011." This project is awarded \textbf{2013 Franz Edelman Finalist for Achievement in Operations Research and Management Science}--the \textbf{Superbowl} competition of optimization and machine learning. I am core member for optimization algorithm design, and I lead the follow-up implementation of other categories.
\item \textbf{Promotion Planning Optimization}: A MILP optimization model was
jointly developed with \textsc{A.T. Kearney} using AIMMS to build promotion plan and
assortment selection to maximize the overall revenue gain. System is
implemented in 2014 and saves about 3 to 5 percent(2 to 5 billions) of the total purchasing cost annually.
%\newline{}
\item \textbf{Forecast and Optimization for Clinics}: The problem is
to accurately forecast the number of patients by type to each clinic.
Sophisticated forecast models that utilize inputs from time, weather, social
media data like Google trend queries are used to predict the number of
visits.These forecasts serve as input to calculate the inventory necessary for
each type of sickness, and the allocation of medical personnel and their
shifts. The overall goal is to improve customer service and increase the number
of clinics from 136 to 500 in three to five years. A nurse scheduling system is also developed to minimize costs.
%\newline{}
\item \textbf{High-Value Pharmacy Inventory Transfer Optimization}:  The problem is to ship 
medical drugs from stores with excess to stores with needs so as to: 1) reduce
potential obsolesces in inventory; 2) better position drugs to meet customer
demand; 3) to aggregate the shipment in such that transportation costs are
reduced. The model is piloted in 121 stores and is expected
to produce \$30 to \$50 million savings as well as reduction in
out-of-stock.
 
%\newline{}
% \item \textbf{Periodic Vehicle Routing}: Each Kroger store has demand that
% fluctuates within a week in various categories, such as frozen, fresh, and
% grocery. Determining the frequency of visit to each store for each category is
% a complex periodic vehicle routing problem. Sophisticated optimization models
% have been built to determine the time of visits for each stores;  these
% optimized visit frequencies are expected to result in a reduction of 10\%
% (equivalent to \$150 million) in transportation cost.
%\newline{}
% \item \textbf{Pharmacy Department Register Simulation}: Each store has a
% different volume in terms of patients visit and service time.The simulation
% model has been created to adjust the number of registers to be installed in
% each store, as a function of service time and customer volume.


\end{itemize}

}

%\bigskip


\bigskip

\cventry{}{Operations Research / Data Science Consultant}
{\textsc{Pro Bono}}{}{}{}{
\begin{itemize}
\item \textbf{NYC Dog Care Stores Weekly Staff Scheduling Optimization}: I helped a dog 
care store with 4 locations to create a weekly staff scheduling system with various 
constraints such as: staff schedule preference, locations preference, demand coverage, and cross-skills satisfaction. 


\item \textbf{Cincinnati Public School Bus Routing Optimization}: I wrote the core 
 optimization algorithm.
  The result is comparable to MIT's solution for the Boston public schools.

\item \textbf{Teaching}:
    I teach Artificial Intelligence and Machine Learning certificate program at University of Texas, Austin collaborated with GreatLearning.com
\end{itemize}


}






%\newpage

%------------------------------------------------
%\cventry{2011.4--2011.8} {Marketing Intern}{\textsc{China Tobacco}}{Beijing,
%China}{}{Conducted intensive marketing analysis for The British American
%Tobacco Co. to broad the Chinese sales channel.}

%\cventry{09.6--09.8,08.6-08.8}{Inventory Management Intern, Business
%Management Intern}{\textsc{The River Seine Food Management }}{Shanghai,
%China}{}{Using ERP to track inventory and reverse logistics. Developed an
%algorithm to re-align the layout of each restaurant according to the daily
%reservation.}


%	AWARDS SECTION

%\begin{comment}
% \section{Awards and Other Information}
% \cvitem{2016}{Last year Ph.D. Assistantships, \textit{College of Engineering
% and Computer Science,Wright State University} }
% \cvitem{2012}{Ph.D. in Engineering Program University Assistantships,
% \textit{College of Engineering and Computer Science,Wright State University} }
% \cvitem{2011}{Provost Enrollment Scholarship, \textit{Wright State University
% Provost Office} }
%\cvitem{2011}{Student International Travel Grant, \textit{Dalian Jiaotong
%University} }
% \cvitem{Citizenship} {P.R.China. H1B Visa Sponsorship needed}
%\end{comment}



%	COMPUTER SKILLS SECTION
%------------------------------------------------------------------------------


\comment{
\section{Languages}

\cvitemwithcomment{Chinese}{Mother tongue}{}
\cvitemwithcomment{English}{Fluent}{IELTS:7}
%------------------------------------------------------------------------------
%	INTERESTS SECTION
%------------------------------------------------------------------------------


\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Trading}{Fishing}
\cvlistdoubleitem{Music Performance}{Long distance running}
\cvlistitem{HIIT}

\comment{
\section{Courses Highlight}
\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
\cvlistdoubleitem{Deterministic O.R. Models}{Stochastic Models for Engineer}
\cvlistdoubleitem{Modern Heuristic}{Integer Programming}
\cvlistdoubleitem{Simulation And Stochastic Models}{Discrete Event Simulation}
\cvlistdoubleitem{Design of Experiment}{Design Optimization}
\cvlistdoubleitem{Probability And Stats}{Data Mining}
\cvlistdoubleitem{Supply Chain Analysis and Design}{Applied Linear Technique}
}


}
\end{document}

